
```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# Introduction


## Motivation

This course aims to provide motivations for learning computational skills and discuss specific examples or ways computational skills could benefit or supplement wet lab work.

## Target Audience  

The course is intended for wet lab researchers who have very little to no computational research experience (for example: users of Excel or GraphPad Prism, but non-"coders")

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.alt="FILL IN TARGET AUDIENCE"}
ottrpal::include_slide("https://docs.google.com/presentation/d/137sOakbsXwN3ovgtlAzZMbQ5a_6ZIg-weTYeQ_Z7DqU/edit#slide=id.g273f0eecfd5_5_25")
```

## Curriculum  

The course covers...

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.alt="FILL IN CONCEPTS DISCUSSED"}
ottrpal::include_slide("https://docs.google.com/presentation/d/137sOakbsXwN3ovgtlAzZMbQ5a_6ZIg-weTYeQ_Z7DqU/edit#slide=id.g273f0eecfd5_5_0")
```

## Objectives

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.alt="FILL IN OBJECTIVES"}
ottrpal::include_slide("https://docs.google.com/presentation/d/137sOakbsXwN3ovgtlAzZMbQ5a_6ZIg-weTYeQ_Z7DqU/edit#slide=id.g273f3ba2b3c_1_292")
```

```{r}
devtools::session_info()
```
