```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```
# The who, what, when, where, and why of Computational Biology

## Learning Objectives

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.alt="FILL IN LOs"}
ottrpal::include_slide("https://docs.google.com/presentation/d/137sOakbsXwN3ovgtlAzZMbQ5a_6ZIg-weTYeQ_Z7DqU/edit#slide=id.g27401a19bd8_1_0")
```

## What are computational biology and data science?

## Motivations for computational work in general and to learn computational skills yourself

## Examples of the application of computational work to wet lab research

## The philosophies and best practices of computational work

### Rigor and ethics in computational work

## Which computational skills are the most important to prioritize learning as a wet lab scientist

### Data Wrangling

### Data Visualization

### Reproducibility and Transparency

### Sharing and reusing public data, code, or tools

## Summary

In conclusion, the benefits of knowing computational skills as a wet lab scientist ...

```{r, echo=FALSE, fig.align='center', out.width="100%", fig.alt="There are benefits to learning computational skills as a wet lab scientist!"}
ottrpal::include_slide("https://docs.google.com/presentation/d/137sOakbsXwN3ovgtlAzZMbQ5a_6ZIg-weTYeQ_Z7DqU/edit#slide=id.g273f0ffd840_0_3")
```

Rather than a scientist being a wet-lab researcher or a dry-lab researcher, in the future we hope scientists have and utilize lab and computational skills for their research.
